The effects of binarity on planet occurrence rates measured by transit surveys

### 2017-10-21 paper/model_2.tex
paper: begin model #3 section

To write the apparent rate density as a function of the apparent 
radius $r_a$, we marginalize out the planet period, semimajor axis, and 
stellar radius (or equivalently the mass ratio, for binaries):
\begin{equation}
\Gamma_a(r_a) =
w_a \Lambda_0 \delta(r_p)
+
w_b \Lambda_1 I_1(r_a)
+
w_b \Lambda_2 I_2(r_a),
\label{eq:model2_Gamma_a}
\end{equation}
where the detection efficiencies are given in 
Eqs.~\ref{eq:detection_efficiency_0}-\ref{eq:detection_efficiency_2}, and as 
in the first model, $w_a=N_0/(N_0+N_1)$, $w_b=N_1/(N_0+N_1)$. The ratio of 
primaries to singles, $\mu$, is now given by a variant of 
Eq.~\ref{eq:mu_definition}:
\begin{equation}
\mu \equiv \frac{N_1}{N_0} = \frac{\rm BF}{1 - {\rm BF}} \left(2^{3/2} - 
\int_{1}^{\sqrt{2}} u^2 (u^2 -1)^{1/\alpha} \,{\rm d}u\right),
\label{eq:mu_model_2}
\end{equation}
where the latter dimensionless integral is easily found numerically.
The $I_1(r_a)$ and $I_2(r_a)$ terms marginalize over the joint distribution of 
apparent radius and mass ratio:
\begin{align}
I_i(r_a) &= 
\int_0^1 p({\rm has\ detected\ planet}, r_a, q | {\rm star\ is\ type\ }i)
    \,{\rm d}q,
\quad
{\rm for}\ i\in\{1, 2\}, \\
&=
\int_0^1 
    p({\rm has\ detected\ planet} | r_a, q, {\rm star\ is\ type\ }i) 
    \nonumber\\
    &\quad\quad\quad\quad\times p(r_a | q, {\rm star\ is\ type\ }i)
    \,p(q | {\rm star\ is\ type\ }i)
\,{\rm d}q.
\end{align}
The first term is the detection efficiency; the second is a $\delta$-function 
of the apparent radius; the latter is the mass ratio distribution given by 
Eq.~\ref{eq:model_2_p_2}.
The analytic solution for $i=1$ is
\begin{equation}
I_1(r_a) = \frac{1}{\mathcal{N}_1} \left(\frac{r_p}{r_a}\right)^{-3}
\left( \left(\frac{r_p}{r_a}\right)^2 -1  
    \right)^{\frac{\gamma+\beta}{\alpha}},
\quad {\rm for}\ r_p/\sqrt{2} < r_a < r_p,
\end{equation}
where $\mathcal{N}_1$ is the normalization term of the binary mass ratio 
distribution (Eq.~\ref{eq:model_2_p_2}): $\mathcal{N}_1 = \int_0^1 
q^{\gamma+\beta} (1+q^\alpha)^{3/2} {\rm d}q$.

>>>>

To write the apparent rate density as a function of the apparent 
radius $r_a$, we marginalize out the planet period, semimajor axis, and 
stellar radius (or equivalently the mass ratio, for binaries):
\begin{equation}
\Gamma_a(r_a) =
w_a \Lambda_0 \delta(r_p)
+
w_b \Lambda_1 I_1(r_a)
+
w_b \Lambda_2 I_2(r_a),
\label{eq:model2_Gamma_a}
\end{equation}
where the detection efficiencies are given in 
Eqs.~\ref{eq:detection_efficiency_0}-\ref{eq:detection_efficiency_2}, and as 
in the first model, $w_a=N_0/(N_0+N_1)$, $w_b=N_1/(N_0+N_1)$. The ratio of 
primaries to singles, $\mu$, is now given by a variant of 
Eq.~\ref{eq:mu_definition}:
\begin{equation}
\mu \equiv \frac{N_1}{N_0} = \frac{\rm BF}{1 - {\rm BF}} \left(2^{3/2} - 
\int_{1}^{\sqrt{2}} u^2 (u^2 -1)^{1/\alpha} \,{\rm d}u\right),
\label{eq:mu_model_2}
\end{equation}
where the latter dimensionless integral is easily found numerically.
The $I_1(r_a)$ and $I_2(r_a)$ terms marginalize over the joint distribution of 
apparent radius and mass ratio:
\begin{align}
I_i(r_a) &= 
\int_0^1 p({\rm has\ detected\ planet}, r_a, q | {\rm star\ is\ type\ }i)
    \,{\rm d}q,
\quad
{\rm for}\ i\in\{1, 2\}, \\
&=
\int_0^1 
    p({\rm has\ detected\ planet} | r_a, q, {\rm star\ is\ type\ }i) 
    \nonumber\\
    &\quad\quad\quad\quad\times p(r_a | q, {\rm star\ is\ type\ }i)
    \,p(q | {\rm star\ is\ type\ }i)
\,{\rm d}q.
\end{align}
The first term is the detection efficiency; the second is a $\delta$-function 
of the apparent radius; the last is the mass ratio distribution given by 
Eq.~\ref{eq:model_2_p_2}.
The analytic solution for $i=1$ is
\begin{equation}
I_1(r_a) = \frac{1}{\mathcal{N}_1} \left(\frac{r_p}{r_a}\right)^{-3}
\left( \left(\frac{r_p}{r_a}\right)^2 -1  
    \right)^{\frac{\gamma+\beta}{\alpha}},
\quad {\rm for}\ r_p/\sqrt{2} < r_a < r_p,
\end{equation}
where $\mathcal{N}_1$ is the normalization term of the binary mass ratio 
distribution (Eq.~\ref{eq:model_2_p_2}): $\mathcal{N}_1 = \int_0^1 
q^{\gamma+\beta} (1+q^\alpha)^{3/2} {\rm d}q$.

### 2017-10-21 paper/model_3.tex
paper: begin model #3 section

See Fig.~\ref{fig:errcases_model_3_log}.

>>>>

In this model, as in the previous one, all single and primary stars have 
identical properties.
Only the secondaries have masses, radii, and luminosities that vary between 
systems: $M\propto R \propto L^{1/\alpha}$.
The radii of planets are assigned independently of any host system
property, and are sampled from an intrinsic radius distribution, which we take 
as
\begin{align}
p_r(r)
&\propto
\left.
\begin{cases}
r^\delta & \text{for } r\geq 2R_\oplus \\
{\rm constant} & \text{for } r\leq2R_\oplus.
\end{cases}
\right.
\label{eq:model3_radius_distribution}
\end{align}
Following Howard et al. (2012)'s measurement, we take $\delta = -2.92$.
Our ``nominal model'' remains the same: the binary fraction is 0.44, 
$\alpha=\beta=\gamma=0$.
We take $\Lambda_i$, the occurrence rate integrated over all possible phase 
space for the $i^{\rm th}$ system type, to be equal for singles, primaries, 
and secondaries.

For this model, we forgo analytic development and focus only on numerics 
(Sec.~\ref{sec:numerical_methods}).
The nominal results are shown in Fig.~\ref{fig:errcases_model_3_log}.
For the assumed planetary and stellar distributions, the inferred rate is 
underestimated over all radii.
Taking Fig.~\ref{fig:errcases_model_3_log} and counting the number of planets 
per star with $r>8R_\oplus$, we can compare the true and inferred hot Jupiter 
occurrence rates.
Under the previously described assumptions, the true rate is 9.1 hot Jupiters 
per thousand stars.
The inferred rate is 6.9 per thousand stars.
This means that the inferred rate underestimates the true rate by a 
multiplicative factor of $\sim 1.3$.
This number is suggestively close to the claimed discrepancy between 
hot Jupiter occurrence rates measured by radial velocity and transit surveys 
(Wright et al. 2012).

However, this result only applies under the assumption that $\Lambda_0 = 
\Lambda_1 = \Lambda_2$.
Given that hot Jupiters are thought to be less common around less-massive 
stars, it would be more sensible to consider $\Lambda_2<\Lambda_0$, while 
letting single stars and primaries host planets at the same rate.
We show the HJ multiplicative correction factor as a function of 
$\Lambda_2/\Lambda_0$ in Fig BLAH.
